Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-10-02 manuscript-figures.Rmd
indicate where CTwidth = 0 in CTmin/max plots

CTmin_df <- data.CT %>%
  filter(variable == "CTmin") %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, median) %>%
  ungroup() %>%
  # Assign a value for cases where R0<1 for all temperatures
  mutate(median_proxy = ifelse(is.finite(median), median, 100))

@@

maxCTmin <- ceiling(max(filter(CTmin_df, is.finite(median))$median))

@@

CTmin_heat_plots <- CTmin_df %>%
  select(-median) %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmin_df,
      sigmaH_proxy < 10^2.2
    ),
    breaks = CTmin_breaks
  ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmin_df,
      sigmaH_proxy > 10^2.4,
      sigmaH_proxy < infinite_divide
    ),
    breaks = CTmin_breaks
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
  scale_fill_manual(
    name = "Critical thermal minimum (°C)",
    values = c(viridis(9), "grey", "grey"),
    labels = ~ ifelse(.x < maxCTmin, .x, "n/a")
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

CTmax_df <- data.CT %>%
  filter(variable == "CTmax") %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, median) %>%
  ungroup() %>%
  # Assign a value for cases where R0<1 for all temperatures
  mutate(median_proxy = ifelse(is.finite(median), median, -100))

@@

minCTmax <- floor(min(filter(CTmax_df, is.finite(median))$median))

@@

CTmax_heat_plots <- CTmax_df %>%
  select(-median) %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmax_df,
      sigmaH_proxy < 10^2.2
    ),
    breaks = CTmax_breaks
  ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmax_df,
      sigmaH_proxy > 10^2.4,
      sigmaH_proxy < infinite_divide
    ),
    breaks = CTmax_breaks
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
  scale_fill_manual(
    name = "Critical thermal maximum (°C)",
    values = c("grey", viridis(9)),
    labels = ~ ifelse(.x < minCTmax - 1, "n/a", .x)
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

>>>>

CTmin_df <- data.CT %>%
  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
  pivot_wider(names_from = variable, values_from = median) %>% 
  # If CTwidth is essentially zero, set CTmin to Inf indicating R0 < 1
  mutate(CTmin = if_else(CTwidth < eps, Inf, CTmin)) %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, CTmin) %>%
  ungroup() %>%
  # Assign a value for cases where R0<1 for all temperatures
  mutate(CTmin = ifelse(is.finite(CTmin), CTmin, 100))

@@

maxCTmin <- ceiling(max(filter(CTmin_df, CTmin<100)$CTmin))

@@

CTmin_heat_plots <- CTmin_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmin)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmin_df,
      sigmaH_proxy < 10^2.2
    ),
    breaks = CTmin_breaks
  ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmin_df,
      sigmaH_proxy > 10^2.4,
      sigmaH_proxy < infinite_divide
    ),
    breaks = CTmin_breaks
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
  scale_fill_manual(
    name = "Critical thermal minimum (°C)",
    values = c(viridis(9), "grey", "grey"),
    labels = ~ ifelse(.x < maxCTmin, .x, "n/a")
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

CTmax_df <- data.CT %>%
  select(sigmaH, KH, Model, system_ID, variable, median, system_label) %>% 
  pivot_wider(names_from = variable, values_from = median) %>% 
  # If CTwidth is essentially zero, set CTmax to -Inf indicating R0 < 1
  mutate(CTmax = if_else(CTwidth < eps, Inf, CTmax)) %>%
  mutate(sigmaH_proxy = sigmaH) %>%
  # Arrange along the plotting variables
  arrange(system_ID, KH, sigmaH_proxy, CTmax) %>%
  ungroup() %>%
  # Assign a value for cases where R0<1 for all temperatures
  mutate(CTmax = ifelse(is.finite(CTmax), CTmax, -100))

@@

minCTmax <- floor(min(filter(CTmax_df, CTmax>0)$CTmax))

@@

CTmax_heat_plots <- CTmax_df %>%
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = CTmax)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmax_df,
      sigmaH_proxy < 10^2.2
    ),
    breaks = CTmax_breaks
  ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(
      CTmax_df,
      sigmaH_proxy > 10^2.4,
      sigmaH_proxy < infinite_divide
    ),
    breaks = CTmax_breaks
  ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
  scale_fill_manual(
    name = "Critical thermal maximum (°C)",
    values = c("grey", viridis(9)),
    labels = ~ ifelse(.x < minCTmax - 1, "n/a", .x)
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal(10) +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 10,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
